Research Journal

### 2018-10-21 journal/main.tex

>>>>

\entry{2018}{10}{08}
\subsubsection*{Rome16K Unsupervised Experiments}

\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/rome16kknn0-loss-l2-unsup-true}
  \label{fig:rome16kknn0-loss-l2-unsup-true-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for best performing of this set}
\end{figure}
\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/rome16kknn0-loss-l2-unsup-false}
  \label{fig:rome16kknn0-loss-l2-unsup-false-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for worst performing of this set}
\end{figure}
\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{figures/rome16kknn0-loss-l1-unsup-true}
  \label{fig:rome16kknn0-loss-l1-unsup-true-sub1}
  \caption{Sample embedding, similarity matrix, histogram, and loss curves for random experiment of this set}
\end{figure}
\begin{table}[H]
  \caption{Numerical results}
      \begin{tabular}{|l|c|c|c|} \hline
                                      &  Same Point Similarities  &  Different Point Similarities  \\ \hline
Baseline   & 8.83e-01 $\pm$ 1.26e-01 & 4.67e-01 $\pm$ 1.32e-01 \\ \hline
Data type \texttt{rome16kknn0}, Loss L1, Supervised   & 5.62e-01 $\pm$ 4.12e-01 & 4.63e-02 $\pm$ 1.31e-01 \\ \hline
Data type \texttt{rome16kknn0}, Loss L1, Unsupervised   & 6.89e-01 $\pm$ 3.50e-01 & 5.79e-02 $\pm$ 1.62e-01 \\ \hline
Data type \texttt{rome16kknn0}, Loss L2, Supervised   & 7.84e-01 $\pm$ 2.54e-01 & 3.16e-01 $\pm$ 2.74e-01 \\ \hline
Data type \texttt{rome16kknn0}, Loss L2, Unsupervised   & 7.21e-01 $\pm$ 2.88e-01 & 1.09e-01 $\pm$ 1.45e-01 \\ \hline
      \end{tabular}
      \label{fig:tab1}
\end{table}
